### 2019-03-21 outline/outline.tex
Add annotated bibliography

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here
	\center
	\textsc{\LARGE University of Minnesota}\\[0.35cm]
	\textsc{\Large SENG 5852}\\[1.5cm]
	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
	\textsc{\Large Research Paper Outline}\\[1cm] 
	\textsc{\large\author
		LLue Xiong\\
	}
	\vfill\vfill\vfill
	\large\today
	\vfill
\end{titlepage}

@@

\subsection{Purpose Statement}
Software engineering has for two decades, contemplated and experimented with the concept of distributing software in faster release cycles and have attempted to do so without sacrificing reliability and security. In attempt to achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meets the need of businesses that -- now more than ever -- want to proactively engage and retain customers. The organizational transition to Agile practices demands a large mentality change, requiring individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units as opposed to large modules developed by siloed units.

>>>>

\begin{titlepage} % Suppresses displaying the page number on the title page and the subsequent page counts as page 1
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for horizontal lines, change thickness here
	\center
	\textsc{\LARGE University of Minnesota}\\[0.35cm]
	\textsc{\Large SENG 5852}\\[1.5cm]
	{\huge\bfseries Continuous Integration, Delivery, \& Deployment: Transforming the Software Industry}\\[0.35cm]	
	\textsc{\Large Outline}\\[1cm] 
	\textsc{\large\author
		LLue Xiong\\
	}
	\vfill\vfill\vfill
	\large\today
	\vfill
\end{titlepage}

@@

\subsection{Purpose Statement}
Software engineering has for two decades, contemplated and experimented with the concept of distributing software in faster release cycles and have attempted to do so without sacrificing reliability and security. In attempt to achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meets the need of businesses that -- now more than ever -- want to proactively engage and retain their customers. The organizational transition to Agile practices demands a large mentality change, requiring individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units as opposed to large modules developed by siloed units.
